%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Customer Service Associate} % Job title
    {Lowe's Canada} % Organization
    {Waterloo, Ontario} % Location
    {Oct. 2022 -- Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained in proper lifting techniques to prevent injury and preserve safety of workers and customers.}
        \item {Followed verbal and written instructions to properly move products.}
        \item {Developed knowledge of tools and hardware from working in the hardware department.}
        \item {Helped large volume of customers every day with positve attitude and focus on customer satisfaction.}
        \item {Maintained customer satisfaction with forward-thinking strategies focused on addressing customer needs and resolving concerns.}
        \item {Kept customer spaces clean, neat and organized for maximum appeal.}
        \item {Distributed information to customers and answered quetsions to serve needs and drive sales.}
        \item {Used hand-held scanners and logs to accurately track item movements and locations.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Property Maintenance Worker} % Job title
    {Julen Property Management Co.} % Organization
    {Huntsville, Ontario} % Location
    {Aug. 2019 -- Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed multiple properties in Waterloo, London, and Huntsville, Ontario.}
        \item {Worked with diverse types of weather and ground conditions.}
        \item {Helped with general painting and basic property development projects.}
        \item {Provided expert lawn care, mulching, aerating, and trimming every season.}
        \item {Safe and injury-free planning and execution.}
        \item {Maintained routine landscaping schedules to boost lawn health.}
        \item {Removed weeds, hazards, and debris from common pathways to improve usability.}
        \item{Edged sidewalks, driveways, and landscape features using line trimmer.}
        \item{Loaded and unloaded mowing equipment with load securement conditions.}
        \item{Trimmed greenery, shrubs, and hedges to maintain uniform appearance.}
        \item{Spot-cleaned stains and repaired scuffs or dings to maintain walls.}
        \item{Emptied trashcans and transported waste or collection areas.}
        \item{Worked flexible hours: night, weekend, and holiday shifts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Construction Worker and Property Maintenance Worker} % Job title
    {Canzan Contracting Ltd.} % Organization
    {Baysville, Ontario} % Location
    {Jun. 2019 -- Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Demonstrated safe and proper operation of equipment and tools to prevent harm to self and team members.}
        \item {Utilized hammers, power tools, saws, levels, and fastening devices to complete projects.}
        \item {Safe and injury-free planning and execution.}
        \item {Helped with general painting and basic property development projects.}
        \item {Gathered waste and trash from job sites for placement in refuse containers to keep job sites clean and organized.}
        \item {Loaded, unloaded, and moved material to and from storage and production areas.}
        \item {Spot-cleaned stains and repaired scuffs or dings to maintain furniture and walls.}
        \item {Maintained cleanliness of restrooms by washing down and properly sanitizing walls, floors and toilets.}
        \item {Quickly learned new skills and applied them to daily tasks, improving efficiency and productivity.}
        \item {Worked flexible hours; night, weekend, and holiday shifts.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
