%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Construction Worker Assistant} % Job title
    {Canzan Contracting Ltd.} % Organization
    {St. Cath., N. Bay, Ontario} % Location
    {Aug. 2023, 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted in renovating and constructing The Shoe Company at multiple shopping centres.}
        \item {Supported carpenters with preparing, measuring, framing, and securing components}
        \item {Developed processes to increase productivity, while maintaining workplace safety and standards}
        \item {Expedited project timelines by transporting materials between storage areas and work sites}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Customer Service Associate} % Job title
    {Lowe's Canada} % Organization
    {Waterloo, Ontario} % Location
    {Oct. 2022 -- Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Trained in proper lifting techniques to prevent injury and preserve safety of workers and customers}
        \item {Interacted and helped a large volume of customers daily with a positive approach and service attitude}
        \item {Developed knowledge of software (scanners \& desktop computers), tools and hardware department}
        \item {Provided solutions to customers to serve their needs and drive sales}
      \end{cvitems}
    }


    \vspace{5mm}

  \vspace{-\baselineskip}

%---------------------------------------------------------
  \cventry
    {Property Maintenance Worker} % Job title
    {Julen Property Management Co.} % Organization
    {Huntsville, Ontario} % Location
    {Aug. 2019 -- Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Performed landscaping and general maintenance of multiple properties in London, Huntsville, and Waterloo, Ont.}
        \item{Maintained household equipment and appliances in working order}
        \item{Helped with general painting and basic property development projects}
      \end{cvitems}
    }

    \vspace{0.5mm}
%---------------------------------------------------------
  \cventry
    {Construction Worker and Property Maintenance Worker} % Job title
    {Canzan Contracting Ltd.} % Organization
    {Orillia, Ontario} % Location
    {Jun. 2019 -- Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Assisted in renovating The Shoe Company at West Ridge Place in Orillia}
        \item{Quickly learned new skills and applied them to daily tasks improving efficiency and productivity}
        \item{Supported fabricators with inventory management and workplace housekeeping}
        \item{Promoted safe and secure practices and habits in a dynamic work environment}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
